%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Project}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Developer\enskip|\enskip Tech stack: Clojure} % Job title
    {Message Encryption Engine } % Organization
    {Minneapolis,Minnesota} % Location
    {Mar. 2016 -Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Applied the RSA algorithm to protect sensitive information from leaking outside.}
        \item {Enhanced the security by applying randomized algorithm for the choose of the public key.}
        \item {Developed some unit test to ensure the correctness of the algorithms used in this project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer\enskip|\enskip Tech stack: Clojure} % Job title
    {Ball Bounce Game} % Organization
    {Minneapolis,Minnesota} % Location
    {Apr. 2016 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a mini ball Bounce game in Clojure}
        \item {Utilized existing library Quil combine with ball bounce algorithm and map for sketch.}
        \item{Implemented Ball Bounce algorithm follow by law of physics, and the game will terminates by estimate collision algorithm.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer\enskip|\enskip Tech stack: Java} % Job title
    {Space-efficient Map Implementation} % Organization
    {Minneapolis, Minnesota} % Location
    {Apr. 2016 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented and redesigned Bloom Filter by using bit array which improve the space efficiency.}
        \item{Developed multiple hash function to distribute hash value evenly in the range of 0 and 32.}
        \item{Improved the efficiency of the vocabulary search in Dictionary.} 
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Developer\enskip|\enskip Tech stack: Java} % Job title
    {A simple syntax parser for code} % Organization
    {Minneapolis, Minnesota} % Location
    {Oct. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a compiler’s name table using Java.}
        \item {Utilized varies data structure such as Stack and HashMap to build Symbol Tree}
        \item {Constructed a complex data structures by combined stack with BST algorithm.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
